Web Scraping: attempt 2

### 2017-04-11 Web_Scraping_Final.Rmd

grab_ave_rec_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0("KORD/", link))
  html <- read_html(ss)

>>>>

grab_ave_rec_temps <- function(link, airport){
  s <- html_session("https://www.wunderground.com/history/airport/")
  ss <- s %>% jump_to(paste0(airport, "/", link))
  html <- read_html(ss)
